Replication analysis

### 2020-02-22 analysis/paper.Rmd
Rename replication_analysis.Rmd to paper.Rmd
testing git commits from R Studio to this repo
Changed from setwd() to here(), require(devtools) to library(devtools), and added the originally named data files.

```{r load packages and set working dir, include=TRUE}

#install specific versions of pakages called out in the paper
require(devtools)

@@

```{r set working directory, include=TRUE}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))
getwd()
```

```{r load data, include=TRUE}
# Read the datafile "lances_M" containing a matrix of dimensional data (metric)
#replication file names did not survive publication!
lances_M<-read.csv("Data/1-s2.0-S0305440318306757-mmc2.csv",header=TRUE)
# Read the datafile "lances_GMM" containing a matrix of landmark data (geometric morphometric)
lances_GMM<-read.csv("Data/1-s2.0-S0305440318306757-mmc3.csv",header=TRUE)

@@

# We can test to see if there is an association between centroid size and shape, before conducting further statistical analyses.
# The results are significant, but they cannot be explained by site difference
lances_ANOVA<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine") # Optional right-hand formula for the inclusion of groups; "~site" can be removed to perform ANOVA on whole dataset
# lances_ANOVA<-procD.allometry(shape ~ size, data=lances_geomorph,method="PredLine") # As above, but with "~site" removed
plot(lances_ANOVA)
print(lances_ANOVA)

>>>>

```{r load packages, include=TRUE}
#adding this line as a git test
#install specific versions of pakages called out in the paper
#require(devtools)
library(devtools)

@@

```{r set working directory, include=TRUE}
#setwd(dirname(rstudioapi::getSourceEditorContext()$path))
#getwd()
library(here)
```

```{r load data, include=TRUE}
# Read the datafile "lances_M" containing a matrix of dimensional data (metric)

#replication file names did not survive publication!
#lances_M<-read.csv("Data/1-s2.0-S0305440318306757-mmc2.csv",header=TRUE)
lances_M<-read.csv(here("Data","1-s2.0-S0305440318306757-mmc2.csv"),header=TRUE)

# Read the datafile "lances_GMM" containing a matrix of landmark data (geometric morphometric)
#lances_GMM<-read.csv("Data/1-s2.0-S0305440318306757-mmc3.csv",header=TRUE)
lances_GMM<-read.csv(here("Data","1-s2.0-S0305440318306757-mmc3.csv"),header=TRUE)

@@

# We can test to see if there is an association between centroid size and shape, before conducting further statistical analyses.

# The results are significant, but they cannot be explained by site difference
lances_ANOVA<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine") # Optional right-hand formula for the inclusion of groups; "~site" can be removed to perform ANOVA on whole dataset

# lances_ANOVA<-procD.allometry(shape ~ size, data=lances_geomorph,method="PredLine") # As above, but with "~site" removed
plot(lances_ANOVA)
print(lances_ANOVA)
